Irt plot extra

### 2022-02-22 manuscript.Rmd
Table 3 superscript is added for SW

colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "$SW^{1}$", "Item Total Correlation")

@@

```{r tabDes,results='asis'}
descriptives2 %>% 
apa_table(landscape =T,caption ="Univariate Descriptive Statistics for the 48 Items. All Items Violated Univariate Normality Assumption Assessed by Shapiro–Wilk (SW) Test. The  Item-total Correlation Ranges Between .03-.48", escape =F, font_size = "footnotesize", note = ("$*p<.001$, $^{1}Shapiro–Wilk$ $Statistics$"), align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
```

>>>>

colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW$^{1}$", "Item Total Correlation")

@@

```{r tabDes,results='asis'}
descriptives2 %>% 
apa_table(landscape =T,caption ="Univariate Descriptive Statistics for the 48 Items. All Items Violated Univariate Normality Assumption Assessed by Shapiro–Wilk (SW) Test. The  Item-total Correlation Ranges Between .03-.48", escape =F, font_size = "footnotesize", note = ("$^{*}$p<.001, $^{1}$Shapiro–Wilk Statistics"), align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
```
